Carbonate chemistry at Ny-Ålesund

### 2022-08-22 awipev-CO2.Rmd
more air-sea CO2 flux

```{r, echo = FALSE, message = FALSE, warning = FALSE}
pco2_fb_remos <- d_all %>% 
  dplyr::select(depth, monthd, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
  dplyr::filter(depth < 2) %>% 
  drop_na() %>% 
  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
  geom_point(col="blue", size = 0.5) +
  #geom_text() +
  xlim(180, 420) + ylim(180, 420) +
  labs(title = "pCO2 at ctd temperature",
       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\muatm)$"),
       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-2 m\\phantom{x}($\\muatm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
pco2_fb_remos
ggsave(filename = "figures/pco2_fb_remos.png", plot = pco2_fb_remos, width = 25, height = 25, units = "cm")
```

>>>>

```{r, echo = FALSE, message = FALSE, warning = FALSE}
pco2_fb_remos <- d_all %>% 
  dplyr::select(depth, monthd, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
  dplyr::filter(depth < 4) %>% 
  drop_na() %>% 
  dpl
  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
  geom_point(col="blue", size = 0.5) +
  #geom_text() +
  xlim(180, 420) + ylim(180, 420) +
  labs(title = "pCO2 at ctd temperature",
       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\muatm)$"),
       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-2 m\\phantom{x}($\\muatm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
pco2_fb_remos
ggsave(filename = "figures/pco2_fb_remos.png", plot = pco2_fb_remos, width = 25, height = 25, units = "cm")
```
